Generative Adversarial Networks

### 2017-11-13 cs6735/project/draft.tex
updated background

>>>>

In this minimax version of the loss functions, the generator suffers from a vanishing gradient when the descriminator confidently rejects the generated data. The initial solution proposed by Goodfellow was to train the generator to maximize $log(D(G(z)))$ rather than minimize $log(1-D(G(z)))$ \citep{2014arXiv1406.2661G}; however, even this new cost function does not completly remove the gradients problems \citep{2017arXiv170104862A}.
